Spfy: distributed predictive genomics of E.coli with graph based result linkage

### 2017-08-23 paper-webserver.tex
CHANGE: integrate the cloud compatibility benefit with the comparison with galaxy

\subsection{Deployment to Cloud-Computing Platforms}
% how costs can be saved because using standard web tech means you can deploy to different cloud computing services
Spfy's common infrastructure allows the platform to be deployed to multiple cloud computing services, without need to modify the code.
Docker containerization is supported by Amazon AWS, Google Cloud, ...
Neglibble impact of Docker containers on performance \cite{di2015impact}.
Costs ...

@@

% namely galaxy
Other scientific workflow technologies such as Galaxy \cite{goecks2010galaxy}, Kepler \cite{ludascher2006scientific}, and Taverna \cite{oinn2004taverna} have been applied to bioinformatic tasks.
Galaxy ...
Taverna ...
Kepler ...
To approach the challenge of integrating different bioinformatics programs, Spfy instead uses technologies prevalent in common web services not necessarily related to scientific workflows.
While we prefer to package individual bioinformatics programs using language-agnostic package managers such as Conda \url{https://conda.io/}, we do agree that suites of bioinformatics software benefits from having all dependencies installed and deployable in Docker containers \cite{di2015impact}.
important to have rapid access available for retrieval while maintaining long-term data storage \cite{schatz2015biological}
long term storage is needed to prevent the constant re-computation of the same data, and to provide pre-computed analyses for common predictive genomic analyses needed by the public health, and research community \cite{de2015trends}.
Integrating results from multiple genomes, and examining shared connections, is an area that currently requires more research \cite{fricke2014bacterial},

>>>>

@@

% namely galaxy
Other scientific workflow technologies such as Galaxy \cite{goecks2010galaxy}, Kepler \cite{ludascher2006scientific}, and Taverna \cite{oinn2004taverna} have been applied to bioinformatic tasks.
Galaxy ...
Taverna ...
Kepler ...
To approach the challenge of integrating different bioinformatics programs, Spfy instead uses technologies prevalent in common web services not necessarily related to scientific workflows.
While we prefer to package individual bioinformatics programs using language-agnostic package managers such as Conda \url{https://conda.io/}, we do agree that suites of bioinformatics software benefit from having all dependencies installed and deployable in Docker containers \cite{di2015impact}.
These programs are connected to form a workflow using task queues; a design methodology used to offload long-running or non-instantaneous tasks over available computing infrastructure.
Unlike platforms such as Galaxy which favor a drag-and-drop design for building workflows, Spfy favors a tightly coupled approach explicitedy linking together different bioinformatics programs within the task queue implemntation.
In particular, Spfy uses asynchronous tasks queues which are tripped in response to user requests, thereby allowing immediate responsivity to users on the website, and processes generating human-readable results can be separated from processes handling long-term result storage.

% standard web tech means you can deploy to different cloud computing services
One of the key benefits of using more common-place technologies is the compatibility with other infrastructure resources.
Docker containerization is widely supported by cloud computing services: Amazon Web Services (AWS) \url{https://aws.amazon.com/docker/}, Google Cloud Platform (GCloud) \url{https://cloud.google.com/container-engine/}, and Microsoft Azure \url{https://azure.microsoft.com/en-us/services/container-service/}, and self-hosted cloud computing technologies such as OpenStack \url{https://wiki.openstack.org/wiki/Docker}.
% we may want to sign up for a free trial to give an example of this
Spfy packages compute nodes, which manage a collection of task queue workers, as reproducible Docker containers which can be networked together to form a compute cluster.
Docker containerization has a neglible impact on performance \cite{di2015impact}, and allows the platform to easily scale to demand.
In contrast to Galaxy, Spfy is a targeted approach building a predictive analytics platform for \textit{E. coli} which leverages generic web technologies to favor a responsive, big-data design strategy tackling the challenge \cite{fricke2014bacterial} of integrating results from multiple genomes and examining shared connections.
